>

### 2020-03-17 manuscript/appendix.Rmd
Add submission files
Remove Twitter analysis from manuscript
The models are still estimated and included in the website for future use and reference, but we can exclude them from the paper. Close #1.

---
output:
  html_document:
    keep_md: yes
---

@@

```{r}
pa_models <- read_rds(here("data/pa_models.rds"))
obesity_models <- read_rds(here("data/obesity_models.rds"))
```

@@

lambda <- "$\\lambda$: spatial correlation"
access_terms <- c("Size and Distance", "Tweets",  "Attributes", "10-min walk")

@@

```{r pa-fullmodels, results = "asis"}
texreg(pa_models, digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c(names_for_terms, lambda, access_terms),
       custom.model.names = c("No Access", access_terms),
       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
       label = "tab:pa-fullmodels",
       caption.above = TRUE, include.aic = F, include.lr = F,
       scalebox = 0.7,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```

```{r ob-fullmodels, results="asis"}
texreg(obesity_models, digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c(ob_names, lambda, access_terms),
       custom.model.names = c("No Access", "Size and Distance", "Twitter", "Amenities", "10-Minute Walk"),
       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
       label = "tab:ob-fullmodels",
       caption.above = TRUE, include.aic = F, include.lr = F, scalebox = 0.7,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```

>>>>

---
output:
  pdf_document:
    keep_tex: yes
---

@@

```{r}
pa_models <- read_rds(here("data/pa_models.rds"))
pa_models$Tweets <- NULL
obesity_models <- read_rds(here("data/obesity_models.rds"))
obesity_models$Tweets <- NULL
```

@@

lambda <- "$\\lambda$: spatial correlation"
access_terms <- c("Size and Distance", "Attributes", "10-min walk")

@@

\begin{table*}
  \caption{\label{tab:pa-fullmodels} Estimated Effect of Accessibility on Physical Activity Rates}
  \begin{center}
  \scalebox{0.7}{
```{r pa-fullmodels, results = "asis"}
texreg(pa_models, digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c(names_for_terms, lambda, access_terms),
       custom.model.names = c("No Access", access_terms), table = F,
       caption.above = TRUE, include.aic = F, include.lr = F,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```
}\end{center}
\end{table*}

\begin{table*}
  \caption{\label{tab:ob-fullmodels} Estimated Effect of Accessibility on Obesity Rates}
  \begin{center}
  \scalebox{0.7}{
```{r ob-fullmodels, results="asis"}
texreg(obesity_models, digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c(ob_names, lambda, access_terms),
       custom.model.names = c("No Access", access_terms), table = F,
       caption.above = TRUE, include.aic = F, include.lr = F, 
       custom.note = "%stars 95\\% confidence interval in brackets.")
```
}\end{center}
\end{table*}

### 2020-03-17 manuscript/manuscript.Rmd
Remove Twitter analysis from manuscript
The models are still estimated and included in the website for future use and reference, but we can exclude them from the paper. Close #1.

To this dataset of parks and regularized green spaces, we add a polygons layer of
cemeteries in New York that are open to the public. Cemeteries are important
green spaces that can be used for many types of physical activity. These
operations leave us with `r nrow(parks)` distinct green spaces; for simplicity 
we will refer to both parks and cemeteries as "parks" going forward. 
For each park, 
we calculate the size of the park in acres. Finally, using a Twitter application
programming interface (API) implemented with the Python package Tweepy,  we also
collected and stored tweets containing geotags of precise geographic coordinates
located within the boundaries of the parks; from this information,
we were able to segregate tweets that were generated within a park in September
2014. This geolocated twitter activity could provide an additional point of information
on the degree to which individual parks are actually used [@Wang2016].

@@

park_summary <- parks %>%
  st_set_geometry(NULL) %>%
  # TODO: This should be tweets
  dplyr::select(acres, courts, playgrounds, trails, tweet_count) %>% 
  gather(variable, value) %>%
  group_by(variable) %>%
  summarise(
    min = min(value),
    `msd` = paste(median_iqr(value)),
    max = max(value)
  ) %>%
  mutate(
    variable = c("Size: Park size in acres",
                 "Courts: Presence of sport courts / ball fields",
                 "Playgrounds: Presence of playgrounds",
                 "Trails: Presence of trails",
                 "Tweets: Tweets emanating from park in September 2014"),
    source = c(rep("NYC", 4), "Twitter API")
    )

@@

We calculate a set of utility-based accessibility statistics for each tract
in New York City. The most basic utility specification includes only the
park size in acres and the distance from the population-weighted tract centroid
to the boundary of the park in miles,
\begin{equation}\label{eq:u_access}
V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
\end{equation}
The logarithmic transform allows for diminishing marginal utility of distance
and park size: A 1-mile increase to a trip matters more for a 1-mile trip than a
10-mile trip. @Macfarlane2019 estimated destination choice 
parameters for park trips in Alameda County (Oakland), California by applying
this utility specification to passively collected mobile device data, obtaining values of $\lambda_s = 0.373$ and 
$\lambda_d = -1.76$. The ratio of these estimates implies people are willing to
travel roughly six times further to reach a park twice as large. We do not have
access to the necessary data to repeat the @Macfarlane2019 methodology in New
York, and the public parks datasets in Alameda County are
not sufficiently detailed to perform the present accessibility analysis there.
In the absence of park trip destination choice coefficients in New York City, we
adopt these previous estimates.

@@

The third utility specification includes the number of geolocated tweets
emanating from within the park in September of 2014 in addition to the
size and distance terms in Equation \ref{eq:u_access},
\begin{equation}\label{eq:u_tweets}
\begin{split}
V_{ij} &= \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \\ 
  &\quad \lambda_{tw} * YJ(tweets)
\end{split}
\end{equation}
with $YJ(x)$ being a Yeo-Johnson transformation that implements a diminishing
marginal return similar to $log(x)$, but where $YJ(0) = 0$ [@Yeo2000]. In this
case we have no external information describing how destination choice to
parks may be affected by the twitter activity in the park, so we assert a 
value of $\lambda_{tw} = 0.1$

@@

```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized utility-based park accessibility values in New York City."}
library(ggmap)
map <- ggmap(
  get_stamenmap(unname(st_bbox(tracts)), 
                maptype = "toner-lite"), extent = "device")
map +
  geom_sf(data = tracts, inherit.aes=FALSE,
          aes(fill = cut(access_ls, breaks = c(-Inf, -3, -2, -1, 0, 1, 2, 3, Inf))),
          alpha = 0.9, color = NA) +
  scale_fill_brewer("Accessibility", palette = "RdYlBu")
```

@@

Table \ref{tab:pa-models} presents the estimated spatial lag and accessibility
coefficients for three models using different specifications of the utility
equation, as well as the ten-minute walk buffer calculated by ParkScore. 
Note that the model called "Size and Distance" is precisely the model
labeled "SDEM" in Table \ref{tab:slx-sdem}. The controlling covariates are
suppressed for clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in the Appendix. Each of the three
utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
and is of the hypothesized directionality. That is, residents living in tracts 
with increased utility-based accessiblity to green spaces show a significantly
higher physical activity participation rate. Taking the rough mean of the three
estimated utility-based coefficients, moving from the least-accessible tract
($A_i = -3$) to the
most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
by `r 6 * .2` percentage points. With the understanding of the full 95\% confidence
interval, we could suggest that the true effect of excellent versus poor park access
is anywhere between `r 6 * .05` and `r 6 * .35` percentage points.

The 10-minute walk buffer is considerably less useful at isolating the effects
of park "access" on physical activity rates. As so few tracts are located
outside of the buffer, the standard error of the estimated effect is large and implies
an effect on activity rates anywhere from a loss of `r 6 * .37` percentage points
to a gain of `r 6 * 1.5`.

\begin{table*}
\caption{Estimated Effect of Accessibility on Physical Activity Rates}
\label{tab:pa-models}
```{r pa-models, results = "asis"}
texreg(pa_models[c(2:5)], digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "10-Minute Walk"),
       custom.coef.map = list(
         "lambda" = "$\\lambda$: spatial correlation", 
         "access_ls" = "Size and Distance", 
         "multi_ls" = "Amenities", 
         "tweets_ls" = "Twitter Activity", 
         "walk_10TRUE" = "10-minute walk"),
       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
       label = "tab:pa-models", table = FALSE,
       caption.above = TRUE, include.aic = F, include.lr = F,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```
\end{table*}

@@

\begin{table*}
\caption{Estimated Effect of Accessibility on Obesity Rates}
\label{tab:obesity-models}
```{r obesity-models, results="asis"}
texreg(obesity_models[c(2:5)], digits = 4, ci.force = TRUE, 
       booktabs = TRUE, use.packages = FALSE, 
       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "10-Minute Walk"),
       custom.coef.map = list(
         "physact" = "Physical Activity", 
         "lag.physact" = "$\\gamma$: Physical Activity",
         "lambda" = "$\\lambda$: spatial correlation", 
         "access_ls" = "Size and Distance", 
         "multi_ls" = "Amenities", 
         "tweets_ls" = "Twitter Activity", 
         "walk_10TRUE" = "10-minute walk"),
       caption = "Estimated Effect of Accessibility on Obesity Rates",
       label = "tab:obesity-models", table = FALSE,
       caption.above = TRUE, include.aic = F, include.lr = F,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```
\end{table*}

@@

This paper applies a previously-presented but little-used accessibility
statistic that could, in theory, accommodate many attributes of the destination
parks as well as the people who might use them. As an illustration: the
park-going population could be separated into at least four delineated clusters,
each preferring different amenities of a park:
\begin{itemize}
 \item{runners and cyclists: long, interesting trail systems}
 \item{sports players: soccer fields, basketball courts, or baseball diamonds}
 \item{families with small children: water features and playgrounds}
 \item{casual users: water features, gardens, performances, etc.}
\end{itemize}
An analyst could then compute the utility-based accessibility for each cluster
with different utility values for each park's amenities, and obtain a measure of
a neighborhood's accessibility to park features that its residents most care
about. In this paper, we proceed only incrementally towards this by adding
Twitter activity and some selected park amenities as an element of each park's 
attractiveness above and beyond its size. Exploring detailed definitions of
an increased number of amenities on one hand, and market segmentation strategies
on the other, could provide a more nuanced understanding of the relationship
between park accessibility and health outcomes.

@@

\begin{acks}
This project was funded by the Speedwell Foundation. We are grateful to Rachel
Samuels and Neda Madi for helping to assemble the geolocated Twitter data.
\end{acks}

>>>>

To this dataset of parks and regularized green spaces, we add a polygons layer of
cemeteries in New York that are open to the public. Cemeteries are important
green spaces that can be used for many types of physical activity. These
operations leave us with `r nrow(parks)` distinct green spaces; for simplicity 
we will refer to both parks and cemeteries as "parks" going forward. 
For each park, we calculate the size of the park in acres.

@@

park_summary <- parks %>%
  st_set_geometry(NULL) %>%
  dplyr::select(acres, courts, playgrounds, trails) %>% 
  gather(variable, value) %>%
  group_by(variable) %>%
  summarise(
    min = min(value),
    `msd` = paste(median_iqr(value)),
    max = max(value)
  ) %>%
  mutate(
    variable = c("Size: Park size in acres",
                 "Courts: Presence of sport courts / ball fields",
                 "Playgrounds: Presence of playgrounds",
                 "Trails: Presence of trails"),
    source = c(rep("NYC", 4))
  )

@@

We calculate a pair of utility-based accessibility statistics for each tract
in New York City. The most basic utility specification includes only the
park size in acres and the distance from the population-weighted tract centroid
to the boundary of the park in miles,
\begin{equation}\label{eq:u_access}
V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
\end{equation}
The logarithmic transform allows for diminishing marginal utility of distance
and park size: A 1-mile increase to a trip matters more for a 1-mile trip than a
10-mile trip. @Macfarlane2019 estimated destination choice 
parameters for park trips in Alameda County (Oakland), California by applying
this utility specification to passively collected mobile device data, obtaining values of $\lambda_s = 0.373$ and 
$\lambda_d = -1.76$. The ratio of these estimates implies people are willing to
travel roughly six times further to reach a park twice as large. We do not have
access to the necessary data to repeat the @Macfarlane2019 methodology in New
York, and the public parks datasets in Alameda County are
not sufficiently detailed to perform the present accessibility analysis there.
In the absence of park trip destination choice coefficients in New York City, we
adopt these previous estimates.

@@

@@

```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized utility-based park accessibility values in New York City."}
library(ggmap)
map <- ggmap(
  get_stamenmap(unname(st_bbox(tracts)), 
                maptype = "toner-lite"), extent = "device")
map +
  geom_sf(data = tracts, inherit.aes=FALSE,
          aes(fill = cut(multi_ls, breaks = c(-Inf, -3, -2, -1, 0, 1, 2, 3, Inf))),
          alpha = 0.9, color = NA) +
  scale_fill_brewer("Accessibility", palette = "RdYlBu")
```

@@

Table \ref{tab:pa-models} presents the estimated spatial lag and accessibility
coefficients for three models using different specifications of the utility
equation, as well as the ten-minute walk buffer calculated by ParkScore. 
Note that the model called "Size and Distance" is precisely the model
labeled "SDEM" in Table \ref{tab:slx-sdem}. The controlling covariates are
suppressed for clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in the Appendix. Each of the three
utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
and is of the hypothesized directionality. That is, residents living in tracts 
with increased utility-based accessiblity to green spaces show a significantly
higher physical activity participation rate. Taking the rough mean of the 2
estimated utility-based coefficients, moving from the least-accessible tract
($A_i = -3$) to the
most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
by `r 6 * .15` percentage points. With the understanding of the full 95\% confidence
interval, we could suggest that the true effect of excellent versus poor park access
is anywhere between `r 6 * .02` and `r 6 * .3` percentage points.

The 10-minute walk buffer is considerably less useful at isolating the effects
of park "access" on physical activity rates. As so few tracts are located
outside of the buffer, the standard error of the estimated effect is large and implies
an effect on activity rates anywhere from a loss of `r 6 * .18` percentage points
to a gain of `r 6 * 1.35`.

\begin{table*}
\caption{Estimated Effect of Accessibility on Physical Activity Rates}
\label{tab:pa-models}
```{r pa-models, results = "asis"}
texreg(pa_models[c(2, 4:5)], digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.model.names = c("Size and Distance", "Amenities", "10-Minute Walk"),
       custom.coef.map = list(
         "lambda" = "$\\lambda$: spatial correlation", 
         "access_ls" = "Size and Distance", 
         "multi_ls" = "Amenities", 
         "walk_10TRUE" = "10-minute walk"),
       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
       label = "tab:pa-models", table = FALSE,
       caption.above = TRUE, include.aic = F, include.lr = F,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```
\end{table*}

@@

\begin{table*}
\caption{Estimated Effect of Accessibility on Obesity Rates}
\label{tab:obesity-models}
```{r obesity-models, results="asis"}
texreg(obesity_models[c(2, 4:5)], digits = 4, ci.force = TRUE, 
       booktabs = TRUE, use.packages = FALSE, 
       custom.model.names = c("Size and Distance", "Amenities", "10-Minute Walk"),
       custom.coef.map = list(
         "physact" = "Physical Activity", 
         "lag.physact" = "$\\gamma$: Physical Activity",
         "lambda" = "$\\lambda$: spatial correlation", 
         "access_ls" = "Size and Distance", 
         "multi_ls" = "Amenities", 
         "walk_10TRUE" = "10-minute walk"),
       caption = "Estimated Effect of Accessibility on Obesity Rates",
       label = "tab:obesity-models", table = FALSE,
       caption.above = TRUE, include.aic = F, include.lr = F,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```
\end{table*}

@@

This paper applies a previously-presented but little-used accessibility
statistic that could, in theory, accommodate many attributes of the destination
parks as well as the people who might use them. As an illustration: the
park-going population could be separated into at least four delineated clusters,
each preferring different amenities of a park:
\begin{itemize}
 \item{runners and cyclists: long, interesting trail systems}
 \item{sports players: soccer fields, basketball courts, or baseball diamonds}
 \item{families with small children: water features and playgrounds}
 \item{casual users: water features, gardens, performances, etc.}
\end{itemize}
An analyst could then compute the utility-based accessibility for each cluster
with different utility values for each park's amenities, and obtain a measure of
a neighborhood's accessibility to park features that its residents most care
about. In this paper, we proceed only incrementally towards this by adding some
selected park amenities as an element of each park's
attractiveness above and beyond its size. Exploring detailed definitions of
an increased number of amenities on one hand, and market segmentation strategies
on the other, could provide a more nuanced understanding of the relationship
between park accessibility and health outcomes.

@@

\begin{acks}
This project was funded by the Speedwell Foundation. We are grateful to Rachel
Samuels and Neda Madi for helping to assemble the data.
\end{acks}
